Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
replaced "tisation" by "tization"

The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesizes correct-by-design
embedded control software. It is based on the description of a physical system
as an equivalent finite-state machine and on the computation of reachability properties over the finite-state 
machine. 
Based on this safety specification over state values, 
Pessoa can synthesize embedded controller software for a range of properties.  
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the ADC/DAC quantisation error needed for
synthesizing fixed-point digital controllers.

@@

We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but enhanced to include evaluation of quantisation effects and safety properties
over the state space. In an alternative approach, we use a verification engine based on abstract acceleration~\cite{cattaruzza2015unbounded}, 
which avoids the explicit unwinding the transition system necessarily for the first approach.

>>>>

The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesizes correct-by-design
embedded control software. It is based on the description of a physical system
as an equivalent finite-state machine and on the computation of reachability properties over the finite-state 
machine. 
Based on this safety specification over state values, 
Pessoa can synthesize embedded controller software for a range of properties.  
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the ADC/DAC quantization error needed for
synthesizing fixed-point digital controllers.

@@

We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and safety properties
over the state space. In an alternative approach, we use a verification engine based on abstract acceleration~\cite{cattaruzza2015unbounded}, 
which avoids the explicit unwinding the transition system necessarily for the first approach.
